Visual Inference for Networks

### 2016-08-02 JSM/VizInfSlides.Rmd
push changes

1. Rate - how often actors change ties 
2. Outdegree - measure of activeness
3. Reciprocity - how often ties are reciprocated
4. Jumping Transitive Triplets

```{r, echo = FALSE}
jTTe <- data.frame(from = c('i', 'i', 'h'), to = c('h', 'j', 'j'))
jTTn <- data.frame(id = letters[8:10], group = c(1,1,2))

@@

## Procedure

Using a subset of the friendship network data from Michell & Amos we:

1. Fit three (XX two? XX) models 1000 times to obtain a distribution of parameter estimates
2. Simulated the second wave from each of our models to form lineups. Means from 1 were used as starting parameter values.
3. Estimated the parameters of each of our three (XX two? XX) models using the simulated second waves.

## ? SOMETHING ELSE ?

# Experiment

## Pilot Study (?)

Help us find a measure of difficulty of a lineup

## Procedure

# Results

>>>>

1. Rate - how often girls change friendships 
2. Outdegree - measure of activeness
3. Reciprocity - how often friendships are reciprocated
4. Jumping Transitive Triplets - friends of the same person become friends

```{r, echo = FALSE, fig.height=2}
jTTe <- data.frame(from = c('i', 'i', 'h'), to = c('h', 'j', 'j'))
jTTn <- data.frame(id = letters[8:10], group = c(1,1,2))

@@

```{r echo=FALSE}
dat <- readr::read_csv("../Lineup-Images/ForExperimentTraining/datafiles/smallfriends-rev-m-12-rep-c.csv")
ggplot(data = dat %>% filter(plot_order2 %in% c(11,12)) %>% mutate(plot = plot_order2 - 10) ) + 
  geom_net(aes(from_id = X1, to_id = X2), size = 2, fiteach = T, directed = T, 
           colour = 'black', arrowsize = .25, arrowgap = .02, ecolour = 'grey60') + 
  facet_wrap(~plot) + 
  theme_net()
```

```{r echo=FALSE}
dat <- readr::read_csv("../Lineup-Images/ForExperimentTraining/datafiles/smallfriends-m-12-rep-1.csv")
ggplot(data = dat %>% filter(plot_order %in% c(2,7)) %>% mutate(plot = ifelse(plot_order == 2, 1, 2))) + 
  geom_net(aes(from_id = X1, to_id = X2), size = 2, fiteach = T, directed = T, 
           colour = 'black', arrowsize = .25, arrowgap = .02, ecolour = 'grey60') + 
  facet_wrap(~plot) + 
  theme_net()
```

## Question

Can we *see* a significant parameter when visualizing networks simulated from two different models?

- Idea: a very statistically significant difference in models should look different to us

## Experiment

- Small Amazon Turk experiment
